Deterministic Scheduling of Periodic Messages in a Network

### 2017-07-19 article/article.tex
mkdir infocom

      In our experiment, we generate $1000$ random instances of PAZL for $1$ to $20$ routes. 
      We measure the average minimal period, for each algorithm. Remind that the exhaustive search always finds the best possible period for a given instance. The lower and upper bound $n\tau$ and $3n\tau$ are also represented.

@@

      \todo{Scalability, is the exhaustive search practical for more routes: conclusion yes for our settings, no if more routes}

@@

      \caption{Success rate of different orders with $P = 21000$}
      \end{minipage} \hfill
        \begin{minipage}[c]{6cm}
          \includegraphics[width=6cm]{departs_gp_30000.pdf}
      \caption{Success rate of different orders with $P = 30000$}

>>>>

      In our experiment, we generate $1000$ random instances of PAZL for $1$ to $12$ routes. 
      We measure the average minimal period, for each algorithm. Remind that the exhaustive search always finds the best possible period for a given instance. The lower and upper bound $n\tau$ and $3n\tau$ are also represented.

@@

      Since the exhaustive search solve PAZL in an FPT time, with parameter $n$ the number of routes, we study the scalability of the time needed by this algorithm, according to $n$. We made an experiment on $100$ random star routed networks, in which the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots. We fixed the period to $n\tau+1000$, that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
         \begin{center}
         \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Number of routes & $1$ & $6$ & $11$& $16$& $21$\\
    \hline
    Average time before answer (ms) & $0.004$ &$0.027$&$0.599$&$59.711$&$14866.1$\\
    \hline
      \end{tabular}
      \end{center}

      With our practical parameters ($n<20$ routes), the algorithm can solve PAZL quickly. As soon as we want to compute more routes, the time required to answer PAZL with the exhaustive search increase exponentially.

@@

      \caption{Success rate of different orders, $95\%$ load.}
      \end{minipage} \hfill
        \begin{minipage}[c]{6cm}
          \includegraphics[width=6cm]{departs_gp_25000.pdf}
      \caption{Success rate of different orders, $80\%$ load.}
